\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-11-26 exps.tex
fig is groupplot

Motor is a stepper motor controller from~\cite{Bourke2009a}, used for
producing monochrome images on paper by applying a correct application
of current to a print head (a row of resistors). In this example,
duration of current applied is controlled by the feedback logic using
real-time delays which are expressed in Esterel constructs. We have
rewritten the program in SystemJ and compared between desired and
relaxed delays according to WCRT and BCRT of the program. Printer is an
example from [], which models a printer and a spooler in timed CSP.
Their operation is rather simple: as soon as the spooler receives a
print job, passes it to the printer through a channel where actual
printing process take place. The example demonstrates that by specifying
delay bounds (e.g. 1 to 5 time units) on receiving and sending channel
ends data exchange will occur as soon as both processes become ready.

@@

HRTCS consists of 2 CDs, but only one with real-time delays. AECS also
has 2 CDs; CD1 consist of a single delay statement, while CD2 has 2
delay statements. In this case, as explained previously, delay
statements replace the external timers and corresponding interface (I/O)
signals. The system triggers an alarm 10 seconds after detection of an
intruder or generates a beep sound when an entrance door is being opened
for the same amount of time. In Printer, each spooler and printer
process is mapped to a single clock-domain. Spooler CD sends a job to
the Printer CD between [] to [] ms after receiving it from the
enviornment (e.g. a user). On the other hand, Printer CD notifies
environment that it starts printing between [] to [] ms once it receives
the job from the Spooler CD. Actual print job is started between [] to
[] after the notification. In this example, bounded delay ensures that
both channel communication and print job should occur within the
specified amount of time. Lastly, Motor is a synchronous program with 5
delay statements where they controls amount of current into the stepper
motor coils.

@@

>>>>

Motor is a stepper motor controller from~\cite{Bourke2009a}, used for
producing monochrome images on paper by applying a correct application
of current to a print head (a row of resistors). In this example,
duration of current applied is controlled by the feedback logic using
real-time delays which are expressed in Esterel constructs. We have
rewritten the program in SystemJ and compared between desired and
relaxed delays according to WCRT and BCRT of the program. Printer is an
example from~\cite{Schneider:1999:CRT:555233}, which models a printer and
a spooler in timed CSP.  Their operation is rather simple: as soon as
the spooler receives a print job, passes it to the printer through a
channel where actual printing process take place. The example
demonstrates that by specifying delay bounds (e.g. 1 to 5 time units) on
receiving and sending channel ends data exchange will occur as soon as
both processes become ready.

@@

HRTCS consists of 2 CDs, but only one with real-time delays. AECS also
has 2 CDs; CD1 consist of a single delay statement, while CD2 has 2
delay statements. In this case, as explained previously, delay
statements replace the external timers and corresponding interface (I/O)
signals. The system triggers an alarm 10 seconds after detection of an
intruder or generates a beep sound when an entrance door is being opened
for the same amount of time. In Printer, each spooler and printer
process is mapped to a single clock-domain. Spooler CD sends a job to
the Printer CD between 2.7 to 10.6 ms after receiving it from the
enviornment (e.g. a user). On the other hand, Printer CD notifies
environment that it starts printing between 1.2 to 30.3 ms once it
receives the job from the Spooler CD. Actual print job is started
between 5.6 to 100.2 ms after the notification. In this example, bounded
delay ensures that both channel communication and print job should occur
within the specified amount of time. Lastly, Motor is a synchronous
program with 5 delay statements where they controls amount of current
into the stepper motor coils.

@@

\subsection{Improving results}

Previous results shows that the compiler was only able to find
\textit{d} for HRTCS and Printer/CD2 without relaxing upper bound.
Figure~\ref{fig:graph} shows the accuracy of our result by comparing
differences between programmer specified upper bounds and the actual
bounds obtained from our algorithm.

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}[scale=0.95]
	\begin{groupplot}[group style={group size=2 by 3,
			xlabels at=edge bottom,
			ylabels at=edge left,
		},
			footnotesize,ybar,xtick=data,
			symbolic x
			coords={HRTCS,Motor,Printer/CD1,Printer/CD2,AECS/CD1,AECS/CD2},
			height=3.3cm,
			xlabel=Benchmark,
			ylabel style={text width=1.4cm},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(-0.15,-3.9)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\nextgroupplot
			\addplot coordinates {(HRTCS,1)};
			\nextgroupplot
			\addplot coordinates {(Motor, 3.54)};
			\addplot coordinates {(Motor, 3.15)};
			\addplot coordinates {(Motor, 4.46)};
			\addplot coordinates {(Motor, 3.35)};
			\addplot coordinates {(Motor, 2.81)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
			\nextgroupplot
			\addplot coordinates {(Printer/CD1, 1.6)};
			\nextgroupplot
			\addplot coordinates {(Printer/CD2, 1)};
			\addplot coordinates {(Printer/CD2, 1)};
			\nextgroupplot
			\addplot coordinates {(AECS/CD1, 4.25)};
			\nextgroupplot
			\addplot coordinates {(AECS/CD2, 4.25)};
			\addplot coordinates {(AECS/CD2, 4.25)};
	\end{groupplot}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph}
\end{figure}
